The Tor Network - Strengths and Weaknesses \\ \Large Computer Security 1 - CS5460 \\ \LaTeX{}

### 2013-11-18 paper.tex
notes to myself, image resources

@@

Javascript vs NoScript, TBB - javascript and cross-scripting

@@

Tor is susceptible to timing attacks. To achieve its low-latency objective, Tor does not explicitly re-order or delay packets within the network.\cite{McCoy2008} Therefore, if an adversary controls both the first hop and the final hop in the Tor circuit then they can use statistical timing tests to become reasonably confident in identifying the activities of the end-user. For example, they could observe 198.51.100.37 connecting to their first node

@@

Does the web server support SSL/TLS? The adversary could fake the server.

@@

It was recently revealed that the National Security Administration (NSA) has been targeting Tor, albeit with marginal success in breaking the anonymity and privacy of its users. However, in early October, the FBI successfully identified and arrested the owner of the Silk Road, a black market operating as a hidden service within the Tor network, and seized the service.

@@

@@

@@

% TODO: use
% http://ieeexplore.ieee.org/stamp/stamp.jsp?tp=&arnumber=4797313
\bibitem{Xin2009}
  Liu Xin, Wang Neng
  \emph{Design Improvement for Tor Against Low-Cost Traffic Attack and Low-Resource Routing Attack}
  2009 International Conference on Communications and Mobile Computing

@@

% TODO: use
% http://ieeexplore.ieee.org/xpls/abs_all.jsp?arnumber=5962653
\bibitem{Ling2011}
  Zhen Ling
  \emph{Equal-Sized Cells Mean Equal-Sized Packets in Tor?}
  IEE International Conference on Communications, 2011

% TODO: use
% http://ac.els-cdn.com/S1389128612003799/1-s2.0-S1389128612003799-main.pdf?_tid=c6751d5e-5009-11e3-9ab2-00000aab0f26&acdnat=1384749046_78b8af8ba2cb2c0a2672840e0c7c5da1
\bibitem{Ling2012}
  Zhen Ling, Junzhou Luo, Wei Yu, Xinwen Fuc, Weijia Jia, Wei Zhao
  \emph{Protocol-level attacks against Tor}
  Computer Networks, 2012

>>>>

(going to expand this a bit more)

@@

(going to expand this a bit more, discuss Javascript vs NoScript, cross-site scripting attacks, TBB defenses)

@@

Tor is susceptible to timing attacks. To achieve its low-latency objective, Tor does not explicitly re-order or delay packets within the network.\cite{McCoy2008} Therefore, if an adversary controls both the first hop and the final hop in the Tor circuit then they can use statistical timing tests to become reasonably confident in identifying the activities of the end-user. %For example, they could observe 198.51.100.37 connecting to their first node

(going to expand this a bit more, add some citations)

@@

(going to expand this a bit more. Does the web server support SSL/TLS? The adversary could fake masquerade as the server)

@@

%It was recently revealed that the National Security Administration (NSA) has been targeting Tor, albeit with marginal success in breaking the anonymity and privacy of its users. However, in early October, the FBI successfully identified and arrested the owner of the Silk Road, a black market operating as a hidden service within the Tor network, and seized the service.

(going to expand this a bit more, discuss NSA, FBI, Silk Road, China, etc)

@@

(going to expand this a bit more and devote the couple pages to this section. I've got IEEE citations like \cite{Xin2009}, \cite{Ling2011}, and \cite{Ling2012} that should be very helpful in demonstrating some weaknesses of Tor

@@

(obviously I need this. Summarize design, attacks, defenses, analysis, reviews in the literature, and then provide my opinion about the future)

% -----------------------------------------------------------------------------

@@

% http://ieeexplore.ieee.org/stamp/stamp.jsp?tp=&arnumber=4797313
\bibitem{Xin2009}
  Liu Xin, Wang Neng
  \emph{Design Improvement for Tor Against Low-Cost Traffic Attack and Low-Resource Routing Attack}
  2009 International Conference on Communications and Mobile Computing

@@

% http://ieeexplore.ieee.org/xpls/abs_all.jsp?arnumber=5962653
\bibitem{Ling2011}
  Zhen Ling
  \emph{Equal-Sized Cells Mean Equal-Sized Packets in Tor?}
  IEE International Conference on Communications, 2011

% http://ac.els-cdn.com/S1389128612003799/1-s2.0-S1389128612003799-main.pdf?_tid=c6751d5e-5009-11e3-9ab2-00000aab0f26&acdnat=1384749046_78b8af8ba2cb2c0a2672840e0c7c5da1
\bibitem{Ling2012}
  Zhen Ling, Junzhou Luo, Wei Yu, Xinwen Fuc, Weijia Jia, Wei Zhao
  \emph{Protocol-level attacks against Tor}
  Computer Networks, 2012
